Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-08 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
fit the paper into 16 pages
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The authors have real PV systems deployed since June $2018$ in a riverside community in the State of Amazonas, Brazil, GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, total $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.

@@

\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) is not the same \cite{Alsadi2018}. Therefore, the comparison must take this issue into account.}

@@

Our novelty relies on a practical approach to pursue the optimal PV systems' optimal solution using contemporary formal methods. The use of formal synthesis to design PV systems has no precedent in literature; we show that our approach results, using seven case studies, are promising. Our synthesis tool can present a solution that is far more detailed and closer to commercial reality than the solution given by the commercial tool. In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is advantageous for our synthesis approach. These technical details are essential for the PV system owner. The industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market.

>>>>

We have real PV systems deployed since June $2018$ in a riverside community in the State of Amazonas, Brazil, GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, total $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.

@@

\textcolor{blue}{An optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) is not the same \cite{Alsadi2018}. Therefore, the comparison must take this issue into account.}

@@

Our novelty relies on a practical approach to pursue the optimal PV systems' optimal solution using contemporary formal methods. The use of formal synthesis to design PV systems has no precedent in literature; we show that our approach results, using seven case studies, are promising. Our synthesis tool can present a solution that is far more detailed and closer to commercial reality than the solution given by the commercial tool. The battery autonomy feature, together with the details of every component of a PV system solution, is advantageous for our synthesis approach; these details are essential for the PV system owner. The industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market.
